Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Use equals instead of equiv

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically-scaled systems to be dynamically identical if certain nondimensional physical
parameters are matched. In the case of fluid systems, the most important
nondimensional parameter is often the Reynolds number, $Re$, which quantifies
the importance of inertial forces over viscous forces on the flow physics
\cite{Acheson1990}: \hl {$Re \equiv Ul/\nu$, } 
%please check the symbol ``\equiv '' and make sure it is correct
where $U$ and $l$ are characteristic
velocity and length scales, respectively, and $\nu$ is the fluid kinematic
viscosity. The~other common dynamical scale, for systems with a free
surface, is the Froude number \hl {$Fr \equiv U/\sqrt{gl}$,}
%please check the symbol ``\equiv '' and make sure it is correct
  where $g$ is the
gravitational acceleration. Matching both the Froude and Reynolds number is not
possible for a scaled model in a given fluid, which is illustrated by the
relation $Re = l^{3/2} g^{1/2} Fr / \nu$, since $Re$ scales linearly with $l$,
or the geometric scale. In general, the geometric scale of a physical model is
not necessarily the same as its dynamical scale. As such, hereafter, we will use
the word ``scale'' to refer to this dynamical scale or the Reynolds number and
assume the Froude number is small enough to be~ negligible.

@@

The performance and wake characteristics of cross-flow (vertical-axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag and operational parameters, such as tip speed ratio, {
 and} on the Reynolds number \cite{Para2002}. Note that an average blade chord
Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
expressed in terms of tip speed ratio \hl {$\lambda \equiv \omega R/ U_\infty$, } 
%please check the symbol ``\equiv '' and make sure it is correct
where
$U_\infty$ is the free stream velocity, $c$ is the blade chord length, $\nu$ is
the fluid kinematic viscosity, $\omega$ is the rotor's angular velocity and $R$
is the rotor radius. The value of $\lambda$ at which a turbine reaches peak
performance in general decreases with turbine solidity $Nc/(\pi D)$
\cite{Templin1974}, which allows for the use of a simpler Reynolds number based
on turbine diameter $Re_D \equiv U_\infty D/\nu$.

@@

We propose a method for predicting the Reynolds number dependence of a cross-flow
turbine using static airfoil characteristics and turbine blade kinematics:
\begin{enumerate}
\item Acquire static lift and drag coefficient data for the desired blade
 profile.
\item For azimuthal angles of 0 to 180 degrees and a given tip speed ratio,
 calculate the geometric angle of attack and relative velocity magnitude from
 the blade and undisturbed free stream velocity \hl {($\equiv 1$)} vectors.
 %please check this symbol
\item With arrays of geometric angle of attack and relative velocity
 magnitude, calculate the blade chordwise force and then the rotor torque
 coefficient from Equations~(\ref{eq:ct}) and (\ref{eq:cc}), respectively.
\item Extract the maximum value of $C_T$, and repeat this process for static
 foil data at multiple $Re$.
\end{enumerate}

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for
geometrically-scaled systems to be dynamically identical if certain
nondimensional physical parameters are matched. In the case of fluid systems,
the most important nondimensional parameter is often the Reynolds number, $Re$,
which quantifies the importance of inertial forces over viscous forces on the
flow physics \cite{Acheson1990}: $Re = Ul/\nu$, where $U$ and $l$ are
characteristic velocity and length scales, respectively, and $\nu$ is the fluid
kinematic viscosity. The~other common dynamical scale, for systems with a free
surface, is the Froude number $Fr = U/\sqrt{gl}$, where $g$ is the gravitational
acceleration. Matching both the Froude and Reynolds number is not possible for a
scaled model in a given fluid, which is illustrated by the relation $Re =
l^{3/2} g^{1/2} Fr / \nu$, since $Re$ scales linearly with $l$, or the geometric
scale. In general, the geometric scale of a physical model is not necessarily
the same as its dynamical scale. As such, hereafter, we will use the word
``scale'' to refer to this dynamical scale or the Reynolds number and assume the
Froude number is small enough to be negligible.

@@

The performance and wake characteristics of cross-flow (vertical-axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag and operational parameters, such as tip speed ratio---and
on the Reynolds number \cite{Para2002}. Note that an average blade chord
Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
expressed in terms of tip speed ratio $\lambda = \omega R/ U_\infty$, where
$U_\infty$ is the free stream velocity, $c$ is the blade chord length, $\nu$ is
the fluid kinematic viscosity, $\omega$ is the rotor's angular velocity and $R$
is the rotor radius. The value of $\lambda$ at which a turbine reaches peak
performance in general decreases with turbine solidity $Nc/(\pi D)$
\cite{Templin1974}, which allows for the use of a simpler Reynolds number based
on turbine diameter $Re_D = U_\infty D/\nu$.

@@

We propose a method for predicting the Reynolds number dependence of a cross-flow
turbine using static airfoil characteristics and turbine blade kinematics:
\begin{enumerate}
    \item Acquire static lift and drag coefficient data for the desired blade
    profile.

    \item For azimuthal angles of 0 to 180 degrees and a given tip speed ratio,
    calculate the geometric angle of attack and relative velocity magnitude from
    the blade and undisturbed free stream velocity (taken as unity) vectors.

    \item With arrays of geometric angle of attack and relative velocity
    magnitude, calculate the blade chordwise force and then the rotor torque
    coefficient from Equations~(\ref{eq:ct}) and (\ref{eq:cc}), respectively.

    \item Extract the maximum value of $C_T$, and repeat this process for static
    foil data at multiple $Re$.
\end{enumerate}
